\section{Bibliografia}

\begin{thebibliography}{99}

\bibitem{studiomapp} 
Sito web dell'azienda Studiomapp.
\\\texttt{https://www.studiomapp.com/en/}
 
\bibitem{CNN} 
Alex Krizhevsky, Ilya Sutskever, Geoffrey E. Hinton.
\textit{ImageNet Classification with Deep Convolutional
Neural Networks}. University of Toronto. 
 
\bibitem{RCNN} 
Ross Girshick, Jeff Donahue, Trevor Darrell, Jitendra Malik.
\textit{Rich feature hierarchies for accurate object detection and semantic segmentation}. UC Berkeley.

\bibitem{fastRCNN} 
Ross Girshick.
\textit{Fast R-CNN}. Microsoft Research. 
 
\bibitem{fasterRCNN} 
Shaoqing Ren, Kaiming He, Ross Girshick, Jian Sun.
\textit{Faster R-CNN: Towards Real-Time Object Detection
with Region Proposal Networks}. Microsoft Research.
 
\bibitem{fasthighresolutiondetection} 
Vıt Ruzicka, Franz Franchetti.
\textit{Fast and accurate object detection in high resolution 4K and 8K video using GPUs}. Carnegie Mellon University.

\bibitem{imagehash}
Mengjuan Fei, Zhaojie Ju, Xiantong Zhen, Jing Li.
\textit{Real-time Visual Tracking Based on Improved Perceptual Hashing}. Zhejiang University, University of Portsmouth, The University of Western Ontario, Nanchang University.

\bibitem{mosse}
David S.Bolme, J.Ross Beveridge, Bruce A.Draper, Yui Man Lui.
\textit{Visual Object Tracking using Adaptive Correlation Filters}. Colorado State University.

\bibitem{goturn}
David Held, Sebastian Thrun, Silvio Savarese.
\textit{Learning to Track at 100 FPS with Deep Regression Networks}. Stanford University.

\bibitem{ssd}
Wei Liu, Dragomir Anguelov, Dumitru Erhan, Christian Szegedy, Scott Reed, Cheng-Yang Fu, Alexander C.Berg.
\textit{SSD: Single Shot MultiBox Detector}. UNC Chapel Hill, Zoox, Google, University of Michigan.

\bibitem{trackingdetection} 
Tracking con detection
\\\texttt{https://towardsdatascience.com/computer-vision-for-tracking-8220759eee85}

\bibitem{kalman} 
Rudolf Emil Kálmán.
\textit{A New Approach to Linear Filtering
and Prediction Problems}. Research Institute for Advanced Study, Baltimore.

\bibitem{hungarian} 
Harold William Kuhn.
\textit{The Hungarian method for the assignment problem}. Princeton University.

\bibitem{hybridboost} 
Yuan Li, Chang Huang, Ram Nevatia.
\textit{LearningtoAssociate: Hybrid Boosted Multi-Target Tracker for Crowded Scene}. University of Southern California.

\bibitem{tensorflow} 
Guida all'utilizzo del framework Tensorflow.
\\\texttt{https://www.tensorflow.org/}

\bibitem{opencv} 
Guida all'utilizzo del modulo OpenCV.
\\\texttt{https://opencv.org/}

\bibitem{numpy} 
Guida all'utilizzo del modulo Numpy.
\\\texttt{https://www.numpy.org/}

\bibitem{matplotlib} 
Guida all'utilizzo del modulo Matplotlib.
\\\texttt{https://matplotlib.org/}

\bibitem{pytest} 
Guida all'utilizzo del modulo Pytest.
\\\texttt{https://docs.pytest.org/en/latest/}

\bibitem{dronechallenge} 
Drone Challenge 2019
\\\texttt{http://aiskyeye.com/views/index}

\bibitem{detectionmetrics} 
Studio delle metriche per l'object detection.
\\\texttt{https://medium.com/@jonathan\_hui/\\
map-mean-average-precision-for-object-detection-45c121a31173}

\bibitem{MOTmetrics} 
Keni Bernardin, Rainer Stiefelhagen
\textit{Evaluating Multiple Object Tracking Performance: The CLEAR MOT Metrics}. Karlsruhe Institute of Technology.

\bibitem{IDF1} 
Ergys Ristani1, Francesco Solera, Roger S. Zou, Rita Cucchiara, Carlo Tomasi.
\textit{Performance Measures and a Data Set for Multi-Target, Multi-Camera Tracking}. Duke University, University of Modena and Reggio Emilia.

\end{thebibliography}